Synthesizing Symmetric Lenses

### 2018-07-11 papers/SymmetricLenses/main.tex
add some changes to optimizations

\paragraph*{Open and Closed Regular Expressions} While \GreedySynth acts
relatively efficiently, it can suffer from an exponential blowup when converting
regular expressions to DNF form. This problem can be mitigated by avoiding the conversion
of some REs to DNF form and by performing the conversion lazily when necessarily.
More specifically, \Expand labels some uncoverted REs as ``closed,'' which means the
type-directed \GreedySynth algorithm treats them as DNF atoms and does not dig into
them recursively.  In other words,
given a pair of closed REs, \GreedySynth can either construct
the identity lens between them (it will do this if they are the same RE), or it can
construct a disconnect lens between them.
Regular expressions that are not annotated as closed are considered ``open.''
%is allowed to to
%map closed regular expressions to each other, but only by using the identity
%lens---they must parse the same string components in all examples.
%This change is easy
%to support by adding non-DNF stochastic regular expressions as a new type of
%``closed'' atom. When converted into a DNF regular expression, if $\Regex$ is
%annotated as ``closed'', then $\ToDNFRegexOf{\Regex} = \AtomToDNFOf{\Regex}$.

\paragraph*{Expansion Inference} Distinguishing between open and closed regular
expressions improves the efficiency of \GreedySynth, but forces \Expand to decide
which closed expressions to open.
At the start of synthesis, all regular expressions are closed. \Expand 
rewrites selected closed regular expressions to
open ones (thereby triggering DNF normalization)
when the disconnect lens is the only lens that will ever apply.

>>>>

\paragraph*{Open and Closed Regular Expressions} While \GreedySynth acts
relatively efficiently, it can suffer from an exponential blowup when converting
regular expressions to DNF form. This problem can be mitigated by avoiding the conversion
of some REs to DNF form and by performing the conversion lazily when necessarily.
More specifically, \Expand labels some uncoverted REs as ``closed,'' which means the
type-directed \GreedySynth algorithm treats them as DNF atoms and does not dig into
them recursively.  In other words,
given a pair of closed REs, \GreedySynth can either construct
the identity lens between them (it will do this if they are the same RE), or it can
construct a disconnect lens between them.
Regular expressions that are not annotated as closed are considered ``open.''

Distinguishing between open and closed regular expressions improves the
efficiency of \GreedySynth, but forces \Expand to decide which closed
expressions to open. At the start of synthesis, all regular expressions are
closed, and \Expand rewrites selected closed regular expressions to open ones
(thereby triggering DNF normalization).
%is allowed to to
%map closed regular expressions to each other, but only by using the identity
%lens---they must parse the same string components in all examples.
%This change is easy
%to support by adding non-DNF stochastic regular expressions as a new type of
%``closed'' atom. When converted into a DNF regular expression, if $\Regex$ is
%annotated as ``closed'', then $\ToDNFRegexOf{\Regex} = \AtomToDNFOf{\Regex}$.

\paragraph*{Expansion Inference} These additional rewrites make the search
through possible regular expressions much harder. Our algorithm automatically
will identify when certain closed regular expressions can \emph{only} be
involved in a disconnect lens.  Such regular expressions will automatically be
opened.
